l

### 2020-02-26 random/career_preparation/resume/resume2.tex
update

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched the applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
    \item \textbf{Link :} github.com/deepskies/cosmoNODE and /dsutils

@@

\textbf{codebyhand: applying handwriting recognition}\\ 
\textbullet{Goal: Use handwriting in IDE and match with code suggestions}\\
\textbullet{Trained convolutional net on Extended MNIST (EMNIST) dataset}\\
\textbullet{Wrote `paint` program that live infers character after each stroke}\\
\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
\textbullet{Todo: character bounding box detection and inference using stroke direction and order}

\begin{itemize}
\item \textbf{Tools:} pytorch, torchvision, torchtext, tkinter 
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/codebyhand
\end{itemize}

\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Preface: I've been making music on my computer for a few years and have uploaded a few hundred tracks by chronology}\\
\textbullet{Goal: Learn generative models like GANs and autoencoders}\\
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM with the encoded }
\begin{itemize}
\item \textbf{Tools:} pytorch, torchaudio, torchvision
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sippyart
\end{itemize}

@@

\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}\\
%-------------------------------------------------------------------------------

>>>>

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
    \item \textbf{Link :} github.com/deepskies/cosmoNODE and /dsutils

@@

\textbf{gym-sips: machine learning in sports betting on google cloud}\\ 
\textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
\textbullet{Trained/tested LSTM model to predict odds and scores on $\sim$$5\times 10^{5}$ rows of 20 features}\\
\textbullet{Created a discrete and continuous action space gym environment where agent either picks one team to place money on or allocates some amount to each}\\
\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
\textbullet{Agent learns to hedge across time and returns a positive reward on test set}

\begin{itemize}
\item \textbf{Tools:} pytorch, gym, spinningup
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips and /gym-sips
\end{itemize}
\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Goal: Learn generative models like GANs and autoencoders}\\
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM}
\begin{itemize}
\item \textbf{Tools:} pytorch, torchaudio, torchvision
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sippyart
\end{itemize}

@@

\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------
